Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets

### 2022-04-16 cover_letter/cover_letter.Rmd
ready to re-submit, check point 1, before switch to rtools
last knit, added motivation letter

---
title: "Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
author: "Wangqian Ju and Heike Hofmann"
date: "10/13/2021"
output:
  pdf_document: default
  html_document: default
---

@@

Wangqian Ju and Heike Hofmann

@@

+   **data** folder: contains data to demonstrate the cmpsR package and reproduce various results in the paper. 
+   **reproducible** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
+   **ju-hofmann_files/figure-latex** folder: contains figures and plots used in the paper

>>>>

---
title: "Motivating Letter for Submission: An Open-Source Implementation of the CMPS Algorithm for Assessing Similarity of Bullets"
date: "10/13/2021"
output:
  pdf_document: default
  html_document: default
---

@@

Wangqian Ju and Heike Hofmann  
Department of Statistics  
Iowa State University  
Ames, Iowa, the United States  
wju@iastate.edu

@@

+   **data** folder: contains data to demonstrate the cmpsR package and reproduce various results in the paper. 
+   **supplementary-files.zip** folder: contains R scripts and data necessary to reproduce all aspects of this submission.
+   **ju-hofmann_files/figure-latex** folder: contains figures and plots used in the paper
